\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-02-01 pdbf-doc.tex
major restructuring - tar support

\section{How to use the PDBF compiler}
Right now there are only two modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the tex file and has the same name as the tex file but ".html" filename extension.\\[8pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|\\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".ova" filename extension.

>>>>

\section{How to use the PDBF compiler}
Right now there are only three modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the tex file and has the same name as the tex file but ".html" as filename extension.\\[8pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|\\[2pt]
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .ova files!
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".ova" as filename extension.
-- The TAR mode which attaches a tar archive file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --tar PDBF_File.html TAR_File.tar|\\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".tar" as filename extension.
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .tar files!
